\begin{transitionframe}{Entry of female workers to Tokyo's civil service}
    \begin{itemize}
        \item Traditionally male dominated sector.
        \begin{itemize}
        \item Less than 2\% of employees were women.
        
        Concentrated in medical departments. \hyperlink{Department}{\beamergotobutton{Gender ratio by department}}

        \vspace{0.5em}
        
        \item Women were hired as contract workers without tenure. \hyperlink{Occupation}{\beamergotobutton{Gender ratio by Occupation}}

        \end{itemize}
    \
    \pause
        
        \item Tokyo's public sector was occupied by disproportionately high-educated employees.\hypertarget{Descriptive}{}

        \begin{itemize}
            \item 40\% of employees graduated from university. 
            
            $\leftarrow$National average: 3\%.
        \end{itemize}         

        
    \end{itemize}
\end{transitionframe}

\begin{transitionframe}{Japan's Conscription System}
    \begin{wideitemize}
        \item Tokyo civil service began losing employees to the Japanese military starting in 1937.

        \item Reservists were required to leave their civilian positions to serve in the military.

        \textit{Reservists}: Veterans who had previously trained or served.

        \begin{itemize}
            \item Approx. 800 employees left their positions during this period.
            \item High level civil servants were exempt from drafting.
        \end{itemize}

        \item Neither reservists nor employers could not predict when reservists would be recalled to active duty.
    \end{wideitemize}
\end{transitionframe}


\begin{frame}{}
\input{Background/BalanceTable31}
\end{frame}
